17th International Satisfiability Modulo Theories Competition (SMT-COMP 2022): Rules and Procedures

### 2022-05-17 rules/rules22.tex
adding Jochen suggestion

A proof checker is considered unsound if it returns \texttt{valid} for
an invalid proof or for a proof containing unchecked steps.  In
particular, if a proof checker can be tricked to return \texttt{valid}
for a satisfiable benchmark, it is unsound.  Thus, a proof checker
must also check that the formula that was proved corresponds to the
benchmark given.  Soundness of the proof checker is a central
criterion by which the participants will be judged.

>>>>

A proof checker is unsound if it returns \texttt{valid} for an (invalid) proof
of a satisfiable benchmark.
%
Thus, a proof checker must also check that the formula that was proved
corresponds to the benchmark given.  Soundness of the proof checker is a central
criterion by which the participants will be judged.
